POMDP comparisons across sigma_m, sigma_g

### 2017-12-13 appendix/appendix.Rmd
set cores dynamically

```{r}
options(mc.cores=9)
```

@@

Because this solution is computationally somewhat intensive, we provide

>>>>

```{r}
options(mc.cores=parallel::detectCores())
```

@@

Because this solution is computationally somewhat intensive, be sure to have ~ 4 GB RAM per core if running the 9 models in parallel.  Alternately, readers can skip the evaluation of this code chunk and read the cached solution from the `policyx` file using the `*_from_log` functions that follow:
